---
title: "class11 section3 onward"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
plot(c(1:10))
```

```{r}
library(bio3d)
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
pdbs <- pdbaln(files, fit = TRUE)
pdbs
```

```{r}
pdbs
```

```{r}
pdbs$ali[1:5, 1:8]
```

```{r}
pdbs$resno[1:5, 1:8]
```

```{r}
# Inspect alignment for gaps
gaps <- gap.inspect(pdbs$ali)
# Indices of non-gap columns
head(gaps$f.inds)
# Access non-gap columns
pdbs$ali[, gaps$f.inds]
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
